### 2022-02-01 Codes/1_geo_ml_simulation.rmd
modified BRF analysis by adding interaction terms

#* source all the R functions in the Functions/R folder
fs::dir_ls(here("Codes", "Functions", "R"), full.names = TRUE) %>%
  purrr::map(~ source(.))

#* source all the python functions in the Functions/Python folder
# source_python(here("Codes", "Functions", "Python"))
# source_python(here("Codes", "Functions", "Python", "run_DML_OF.py"))
# source_python(here("Codes", "Functions", "Python", "run_DR_OF.py"))
# source_python(here("Codes", "Functions", "Python", "run_DML_OF_c.py"))
```

@@

#* Read field data
field_data <-
  readRDS(here("Data/field_data.rds")) %>% .[sce_i, ] %>% 
  pull(field_sf) %>%
  .[[1]]

#* Read field parameters
field_parameters <- readRDS(here("Data/field_parameters.rds")) %>% .[sce_i, ]

@@

#* Read field data
field_with_design <- readRDS(here("Data/field_with_design.rds")) %>% .[sce_i, ]

@@

#* Build spatial weights matrix
# Wls <- readRDS(file = here("Data", "Wls.rds"))
# 
#
#   #*****************************************************************************
# this part should be added to the data preparation codes, and saved in field_data
  dt <- sim_data$reg_data[[1]][sim == 1, ]$data[[1]]
  D <- matrix(NA, nrow(dt), nrow(dt))             # distance matrix
  for (i in 1:nrow(dt)){
      for(j in 1:nrow(dt)){
          D[i,j] <- sqrt((dt$X[i] - dt$X[j])^2+
                             (dt$Y[i] - dt$Y[j])^2 )
      }
  }
  W <- 1/D^2             # inverse distance weights matrix
  diag(W) <- 0
  W <- W/rowSums(W)			    # row-standardize
  Wls <- mat2listw(W)	            # "listw" object
  saveRDS(Wls, file=here("Data","Wls.rds"))
#   #*****************************************************************************
```

>>>>

#* source all the R functions in the Functions/R folder
fs::dir_ls(here("GitControlled", "Codes", "Functions", "R"), full.names = TRUE) %>%
  purrr::map(~ source(.))

@@

#* Read field data
field_data <-
  readRDS(here("Shared/Data/field_data.rds")) %>%
  .[sce_i, ] %>%
  pull(field_sf) %>%
  .[[1]]

#* Read field parameters
field_parameters <- readRDS(here("Shared/Data/field_parameters.rds")) %>% .[sce_i, ]

@@

#* Read field data
field_with_design <- readRDS(here("Shared/Data/field_with_design.rds")) %>% .[sce_i, ]

@@

#* Build spatial weights matrix
# Wls <- readRDS(file = here("Data", "Wls.rds"))
#
#
#   #*****************************************************************************
# this part should be added to the data preparation codes, and saved in field_data
dt <- sim_data$reg_data[[1]][sim == 1, ]$data[[1]]
D <- matrix(NA, nrow(dt), nrow(dt)) # distance matrix
for (i in 1:nrow(dt)) {
  for (j in 1:nrow(dt)) {
    D[i, j] <- sqrt((dt$X[i] - dt$X[j])^2 +
      (dt$Y[i] - dt$Y[j])^2)
  }
}
W <- 1 / D^2 # inverse distance weights matrix
diag(W) <- 0
W <- W / rowSums(W) # row-standardize
Wls <- mat2listw(W) # "listw" object
saveRDS(Wls, file = here("Data", "Wls.rds"))
#   #*****************************************************************************
```
